### 2021-06-21 Strings2020/strings2/strings2.tex
Add minor tweaks to various notes
Update strings with note on finite transformations

@@

	\begin{enumerate}
	\item For simplicity, assume for now $X = X(z)$: holomorphic. Note that the $\alpha'$ term comes from the transformation of \textit{internal} degrees of freedom. We have:
	\begin{gather}
		X'(z') - X(z)
		= -\frac{\alpha' V}{2}\,\pd\epsilon
			+ \order{\epsilon^2},
%		\simeq -\frac{\alpha' V}{2}\,\pqty{
%			\dv{z'}{z} - 1
%		},\\[.5ex]
%		X'(z') - \frac{\alpha' V}{2}
%		\simeq X(z) - \frac{\alpha' V}{2}\,
%			\dv{z'}{z},
%		\\[1ex]
%		X'(z')
%		\simeq X(z) + \frac{\alpha' V}{2}\,\pqty{
%				1 - \pd w + \order{\pd w}^2
%			},
		\label{eq:dilaton_holomorphic}
	\end{gather}
	This is a first order approximation of the finite transformation $z\mapsto z' = w(z)$.

	To obtain a full expression, notice that for the above transformation to be a \textit{symmetry}, the action should be invariant under $X(z)\mapsto X'(z)$:
	\begin{equation}
		S' = S
		\ \Longrightarrow\ %
		\int \dd[2]{z}
			\pd X'^\mu \pdbar X'_\mu (z,\bar{z})
		\xlongequal{(*)} \int \dd[2]{z'}
			\pd' X'^\mu \pdbar' X'_\mu (z',\bar{z}')
		= \int \dd[2]{z}
			\pd X^\mu \pdbar X_\mu (z,\bar{z})
	\end{equation}
	Here at $(*)$ we use the diff-invariant property of the action. 
	Restore the anti-holomorphic component and insert \eqref{eq:dilaton_holomorphic}, then we find that in order to cancel the $\order{\epsilon^2}$ terms, we have to fix:
%	\begin{gather}
%		X'(z',\bar{z}') - \alpha'V
%		\simeq X(z,\bar{z})
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{z'}{z} + \dv{\bar{z}'}{\bar{z}}
%			},\\[1ex]
%		X\longmapsto
%		X'(z,\bar{z})
%		\simeq X\pqty\Big{
%				w^{-1}(z),\bar{w}^{-1}(\bar{z})
%			} + \alpha'V
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{w}{z} + \dv{\bar{w}}{\bar{z}}
%			},
%	\end{gather}
	\begin{equation}
		X'(z') - X(z)
		= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \order{\epsilon^3}
		}
	\end{equation}
	The above process can be done order by order, in the end we obtain that\footnote{
		I would like to thank Lucy Smith for helpful discussions. A better recipe to find finite transformations is to consider its properties under composition, which will lead to some constraints that can be solved to obtain the result. 
	}:
	\begin{equation}
	\begin{aligned}
		X'(z',\bar{z}') - X(z,\bar{z})
		&= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \frac{1}{3}\,(\pd\epsilon)^2
			- \cdots
		} + \pqty{\mrm{conjugate}} \\
		&= -\frac{\alpha' V}{2}\,
			\ln (1 + \pd\epsilon)
		+ \pqty{\mrm{conjugate}} \\[.5ex]
		&= -\frac{\alpha' V}{2}\,
			\ln \pqty{
				\dv{z'}{z}
				\dv{\bar{z}'}{\bar{z}}
			}
	\end{aligned}
	\end{equation}

>>>>

\usepackage{cancel}

@@

	\begin{enumerate}
	\item For simplicity, assume for now $X = X(z)$: holomorphic. Note that the $\alpha'$ term comes from the transformation of ``\textit{internal}'' degrees of freedom, associated with the conformal properties of $X$. We have:
	\begin{gather}
		X'(z') - X(z)
		= -\frac{\alpha' V}{2}\,\pd\epsilon
			+ \order{\epsilon^2}
%		\simeq -\frac{\alpha' V}{2}\,\pqty{
%			\dv{z'}{z} - 1
%		},\\[.5ex]
%		X'(z') - \frac{\alpha' V}{2}
%		\simeq X(z) - \frac{\alpha' V}{2}\,
%			\dv{z'}{z},
%		\\[1ex]
%		X'(z')
%		\simeq X(z) + \frac{\alpha' V}{2}\,\pqty{
%				1 - \pd w + \order{\pd w}^2
%			},
		\label{eq:dilaton_holomorphic}
	\end{gather}
	This is a first order approximation of the finite transformation, where the transformation parameters are the modes $\epsilon_n$ of $\epsilon(z)$; namely, we have:
	\begin{equation}
		w(z) = z + \epsilon(z) + \order{\epsilon^2},
	\quad
		\epsilon(z) = \sum_n \epsilon_n z^n
	\end{equation}
	\vspace{-.5\baselineskip}
	\begin{equation}
		F[w(z)] = X'(z') - X(z)
	\ \xlongrightarrow{w\to 0\,}\ %
		-\frac{\alpha' V}{2}\,\pd\epsilon
			+ \order{\epsilon^2}
	\end{equation}

%	For the finite ``internal'' transformation induced by $w(z)$, 
	What the above actually means is that:
	\begin{equation}
		\fdv{\epsilon_n} F[w(z)]_{\epsilon\to 0}
		= -\frac{\alpha' V}{2}\,\fdv{\epsilon_n}\,
			\pdd{z} \pqty\big{w(z) - z}
		= -\frac{\alpha' V}{2}\,
			n z^{n-1}
	\end{equation}
	Where $\epsilon\to 0$ corresponds to $w \to z$, i.e.~the transformation goes to the identity. 
	On the other hand,
	\begin{equation}
	\begin{aligned}
		\fdv{F}{\epsilon_n}
		&= \pdv{F}{w} \fdv{w}{\epsilon_n}
			+ \pdv{F}{(\pd w)} \fdv{(\pd w)}{\epsilon_n}
			+ \pdv{F}{(\pd^2 w)} \fdv{(\pd^2 w)}{\epsilon_n}
			+ \cdots \\
		&= \pdv{F}{w}\, z^n
			+ \pdv{F}{(\pd w)}\, n z^{n-1}
			+ \pdv{F}{(\pd^2 w)}\, n(n-1)\,z^{n-2}
			+ \cdots
	\end{aligned}
	\end{equation}

	By comparing the two above equations, and noting that $\pdv{F}{(\pd^\bullet w)}$ should have no dependence on $n$, we obtain the following constraints on the form of $F[w(z)]$:
	\begin{equation}
		F|_{w\to z} = 0,
	\quad
		\pdv{F}{w}\bigg|_{w\to z} = 0,
	\quad
		\pdv{F}{(\pd w)}\bigg|_{w\to z}
		= -\frac{\alpha' V}{2},
	\quad
		\pdv{F}{(\pd^k w)}\bigg|_{w\to z} = 0,
	\quad k = 2,3,\cdots
	\end{equation}
	We can think of this as the first order ``Taylor'' coefficients of $F[w]$ in the functional space, around the point $w(z) \to z$. Note that $\pd w|_{w\to z} = 1$, while $
		\pd^k w|_{w\to z} = 0
	$, it is thus natural to consider the following ansatz:
	\begin{equation}
		F = F[\pd w],
	\quad
		F[1] = 0,
	\quad
		\pdv{F[x]}{x}\bigg|_{x\to 1}
		= -\frac{\alpha' V}{2}
	\end{equation}

	In the end we shall obtain that\footnote{
		I would like to thank Lucy Smith for helpful discussions. 
	}:
	\begin{equation}
	\begin{aligned}
		X'(z',\bar{z}') - X(z,\bar{z})
		&= -\frac{\alpha' V}{2}\,
			\ln \pqty{
				\dv{z'}{z}
				\dv{\bar{z}'}{\bar{z}}
			}
	\end{aligned}
	\end{equation}
	A better recipe to find finite transformations is to consider its properties under composition, which will lead to some constraints that can be solved to obtain the result\footnote{
		See \https{bryango.github.io/resources/archive/alpha/schwarzian.pdf} for some detailed discussions.
	}.
